Enhancing the sales prediction of newly published books by means of computational intelligence methods

### 2016-02-06 paper.tex
Modificaciones al texto y varias preguntas para @pacv y @amorag. He borrado mis comentarios anteriores ya resueltos

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
When a new book is launched the publisher faces the problem of
how many books should be printed for delivery to bookstores. Printing too many is the main issue,
since it implies a loss of investment due to inventory excess. In this
paper we are tackling the problem of predicting total sales in order to 
print the right amount of books, doing so even before the book has
reached shelves. 
Several years 
% Antonio - Decir cuántos años son, que no me acuerdo.
of data on published books in Spain have been processed by means of data visualisation and other feature selection techniques. The aim is to find out what are the variables that have more impact on sales, and then use machine learning and forecasting methods to predict sales, and, from them, estimate the print-run.
The described methodology improves the forecasting running time and is eventually able to predict sales with remarkable accuracy. Moreover, the proposed method has been validated by the company that provided the data and incorporated in a business intelligence tool for publishers,
since the obtained models provide a reliable guidance on the decision process of
publishing a book, without human intervention 
either for the operation or for interpretation.
% Antonio - esto es cierto??? :D
\end{abstract}

@@

Publishing a book, as releasing any other product, implies several
types of risks and costs due to
the complexity and derived expenses of the production and distribution processes. 
% tienes que enmarcar el problema. Se trata de productos culturales
% con soporte físico y con ventas relativamente pequeñas. Libros,
% discos, no sé si alguna cosa más. - JJ
A newly launched product could be, additionally, completely new to the company (not a new version or edition of a previous product), and sales forecasts can
only be based on the experience of other similar products. 
In this scope, having accurate estimations of future sales of the new
product is extremely important \cite{ChingChin2010}, so that production
runs do not exceed predicted sales. 
Indeed, several studies have demonstrated that improving sale predictions 
(a reduction of forecasting errors) results in an enhancing in the 
production process \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.

@@

Book publishers, as well as other content producers, release new {\em
  products} more frequently than other industries, so that they face the
problem of predicting sales quite often. The issue, in this case, is to print an
adequate number of copies but not too many, as the unsold volumes will
lead to losses and sunk inventory cost, 
% Antonio - 'sunk inventory cost' es corecto?
whereas if the number of printed copies was not enough, you can always print more. 
% Antonio - Esto habría que matizarlo más, de hecho, decirlo va un poco en contra de nuestro artículo, ya que simplifica el problema. Yo indicaría que errores en predicciones por exceso o por defecto tienen MUCHAS pegas (ambos casos), si bien el exceso es peor, claro, pero decir que lo otro es también muy negativo y por eso hay que ajustar muy bien la predicción. ;)
% Se podría señalar, por ejemplo:
% - repetición de costes de distribución
% - mala impresión al cliente/lector, que pueden repercutir negativamente en las ventas
% - algunas más... :D
In this sense, errors in one or the other direction do not have the same impact, although a temporal scarcity of a book that is selling well is also a problem.
% Antonio - esto habría que rescribirlo de acuerdo a lo anterior que comento. ;)

Thus, it is extremely important to develop an accurate predictive tool which could accurately forecast the future sales a new book will achieve, in order to optimise production and to improve the publishing company profits or minimise losses \cite{Zhao2001}. This is the main objective of this paper.
An example is the optimisation of sales \cite{Mattila2002} by
improving profit margins by selling the whole print-run. 
% Antonio - podrías extender un poco el ejemplo? Es decir, describir un poco más lo que se hace en ese trabajo. ;)

However, designing such an accurate predictive tool is a difficult task in this scope, as book sales are influenced by several factors that make them fluctuate and, moreover, usually they might be not controllable and even unknown. 
For instance, some are related with decisions on purchases, others with freight 
traffic, or others with the distribution strategy \cite{Little1998}.

Thus, it is very important to know the product and the variables that
might affect the sales, and how an expert manager takes them into account \cite{Armstrong2001,SThomassey2014}. 
                                % ¿Esto también pasa en la industria de la
                                % moda. ¿Qué vamos a usar de esto? - JJ
                                % [Pedro] esto iba referido a la Industria Editorial.
Their impact is difficult to estimate and it is not constant over time, 
hence the difficulty to adequately identify and measure their influence \cite{DeToni2000}.
In addition, some may have correlations between them. 
However, these correlations can be detected using data analysis methods, 
such as Self-Organizing Maps (SOM) \cite{kohonen1998} 
or stepwise regression analysis (SRA) \cite{Chang2009}. % What do they do? What are the results?

In this research, the problem of how many units should be printed 
when a new book is published is faced using data provided by the 
Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}},
a company that provides management systems and services for book shops,
% Antonio - 'libraries' o 'book shops'? Supongo que lo segundo. ;D
publishers and distributors. 
Usually, the company's expert sales managers analysed historical data 
and applied their knowledge using external variables to compute correct estimations (predictions), for instance, she can decide increasing or decreasing the sales prediction based on season or sales period.
                        % varias citas - JJ
                        % [Pedro] lo modifico para comentar quienes nos facilitaron los datos
                        %  y que así era como funcionaban hasta ese momento.
%In any case, in general companies usually use a forecasting model and then, 
%an expert applies his knowledge, as the company might require an 
%interpretable and understandable model. 
However, carrying out the analysis and forecasting process as a human expert,
may lead to a `fuzzy-like' analysis, which may not take all the variables into account. 
In addition, the process might be tedious, especially when the amount
of data is quite large, and even, different experts can reach different
predictions from the same dataset \cite{ChingChin2010,Sanders1994}.

@@

Specifically, Time-Series prediction methods \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990} 
is perhaps the most used technique to tackle the sales forecasting problems. 
%FERGU: terminar esta frase con punto en vez de coma para que no sea larga.   OK
The efficiency of these techniques strongly depends on the field of application 
and the correctness of the problem data. However, since they require a large amount of data for predicting sales, these methods are not the most suitable for this task \cite{ChingChin2010}.

@@

For this reason, usually the methods used to predict book sales have been generally based on experts' experience. They analyse data about sales and, taking into account their knowledge in industry, their experience, and their perception about trends, could make decisions on the companies production (how many books should be printed when a new book is published).
This is a complex problem, since the predictions are influenced by external variables that must be taken into account, such as seasonality, promotions or fashions that expert managers might subjectively apply \cite{Lapide1999,ChingChin2010,ChernWSF15}.

  %[pedro] sobre la industria editorial no hay trabajos sobre predicción de ventas.
  % Lo habitual ha sido usar el conocimiento de expertos para realizar predicciones 
  %  o aconsejar acerca de la cantidad de libros a imprimir.
  % Lo más parecido que he encontrado son dos trabajos (uno en realidad) de Moon et al. 
  %  sobre "Use Blog Information As Book Sales Prediction":
  %     Moon2010ICSSSM
  %     Moon2010ICEC
Recently, some works propose analyzing relationships between on-line information 
and book sales \cite{Moon2010ICSSSM,Moon2010ICEC}. Specifically, Moon et al. propose using the number of blog references as an indicator of the success of a book, and thus its sales. Different sales patterns are observed by analysing data obtained.
% Antonio - describir esos 'sales patterns'. ;)
%
However, the authors used in these papers historical data from published books, 
so their proposed methodology can not be applied in the problem of unpublished-books sales prediction.

@@

In order to deal with this issue, i.e. forecasting sales of new products, some authors have used different data mining methods \cite{Hammond1990,Chang2009,ChingChin2010,Thomassey2012,Xia2012}. 
% Antonio - quizá habría que comentar alguno o todos bervemente...
%
In the same line, Thomassey et al. \cite{SThomassey2014} propose using a clustering method together with decision trees for sales forecasting in textile-apparel fashion industry, %FERGU: appared? apparel, creo.  ¡sí!
a very similar issue to the new book publishing one.
The same problem was previously faced by Xia et al. \cite{Xia2012} using a 
forecasting method based on extreme machine learning with adaptive metrics of inputs.
% Antonio - of -> as???
The complexity of this problem relies on the lack of historical data, on the short lifetime of the majority of items, 
% Antonio - ver si está bien el cambio 'large number' -> 'majority'
and on the influence of variables such as promotions, fashions, or economic environment \cite{Thomassey2012,Xia2012,SThomassey2014}, as mentioned above.

  %[Pedro] otro caso muy similar es el paper de ChingChin2010 sobre:
  % New tea product
  % New cosmetic product
  % New soft drink product
In \cite{ChingChin2010}, a decision-support system for new product sales %FERGU: The work of Chinchin et al.?
forecasting is proposed to solve three real-world sales forecasting problems, namely: new tea, cosmetics, and soft drink products. This is addressed taking into account quantitative variables.
% Antonio - qué significa eso?
In that study, products are classified based on their sales patterns, so it is assumed that products in the same class would follow a similar sales pattern. %FERGU: "_a_ similar sales pattern", mejor? ok
However, as the authors state, the proposed system can not deal with qualitative 
data related to the products. Moreover, real-world cases, such as consumer 
electronics and fashion products, should be deeply analyzed, as these industries 
present/launch new products every season.

@@

The main objective of this paper is to forecast sales for 
unpublished books for which no historical data are available. Instead, just some
descriptive and variables known in advance related to the new book. In order to do that, we have used a training dataset which includes historical sales data for a big amount of books published in Spain for several years, with a set of 50 features or variables per pattern.

@@

In this prediction problem there are other external variables that also affect 
the sales of a new book, such as those related to seasonality, trends or 
promotions, that classical prediction methods can not deal with.
However, an expert can consider them to modify the forecast obtained by 
the automatic method. Even publishing companies tend to define rules or 
indexes to subjectively adjust the results of prediction based on
external data. 
Thus, the proposed method, will analyse the provided data and variables and will yield a forecast of sales according to them. This result could be used as a reference for a human expert, who would consider it in his/her own prediction process.

@@

There is no a standard methodology to solve the general problem of sales forecasting. %FERGU: hacer más hincapié de esto en la intro entonces
In this work we have followed these steps:
%\hspace{2cm}
\begin{verbatim}
  Step 1: Collect and analyse data
       - Data preprocessing
       - Feature selection
  Step 2: Select the best forecasting method
       - Evaluate forecasting models
       - Perform forecast
  Step 3: Subjectively adjust obtained results
      - Apply additional expert knowledge, such as information 
        about seasonality or trends.
\end{verbatim}

@@

Then, a Feature Selection process \cite{kittler1986feature} is carried out, as it is an effective dimensionality reduction technique and an essential preprocessing method to remove `noisy' (non-useful) features \cite{Krishnapuram2004}. The aim of these algorithms is exploring the space of attributes to find out which subset of them yield the best results in a classification or prediction problem.
  In this stage, both, numerical and visualisation-based approaches has been applied, in order to select the best variables for the forecasting methods.
  This task may also help to identify leading indicators to be considered by a human expert ti do predictions.

After this process, several forecasting methods have been tested, considering different approaches, such as rule- or tree-based, together with numerical methods. 
% Antonio - is 'numerical' the best term for these kind of methods?
The obtained results are then compared.

@@

In the literature different error measures can be found to evaluate the results obtained using the prediction methods \cite{ChingChin2010,Madsen2008}. 
Those error measurements are also called error functions or cost functions. 
%One of the most commonly used is the mean absolute error (see equation \ref{eq:MAE}).
We have used the widely accepted standard equations \cite{gepsoft} in order to compare the obtained results with those presented in other research papers using other methods.
That is why different standard error measurements (Equations \ref{eq:MAE} to \ref{eq:RRSE}), implemented in tools like Weka \cite{pentaho,Witten2011} 
or R \cite{otexts,Hyndman2013}, are considered.
Specifically, in order to compute the forecasting errors of the different methods, Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute error (RAE) and Root relative squared error (RRSE) have been selected:

@@

%-------------------------------------------------
\subsection{Data collection and analysis}

@@

Feature extraction is a ``transformation-based approach'', therefore it transforms the original meaning of the features. This approach involves creating a subset of new features by combinations of the existing features, thus is employed when the semantics of the original dataset will not be needed by any future process. On the contrary, feature selection attempts to retain the meaning of the original feature set. It is part of what is called semantic-preserving techniques, known as ``selection-based approaches". By searching through all possible combinations of features, the aim of these techniques is to determine a minimal feature subset to reduce processing time, while obtaining the same or higher accuracy as the initial feature set \cite{liu1998feature}. In the problem this work assesses, it is very important to maintain the semantics of the set of initial variables, and therefore several feature selection methods have been applied.

@@

SOMs (and U-Matrix) are usually applied for visualise natural structures in the data and their relations, as well as the natural groupings that could be among them. In addition, SOM makes easy the estimation of the variables that have more influence on these groupings. Other statistical and soft computing tools can also be used for this purpose, but since Kohonen's SOMs offers a visual way of doing it, it is much more intuitive, and takes advantage of the capabilities of the human brain as a pattern recogniser.

@@

As far as the feature selection methods are concerned, Weka separates the process in two parts:
\begin{itemize}
  \item Attribute evaluator: This is the method by which the feature subsets are assessed. In this work, both a correlation-based feature subset evaluation method (CfsSubsetEval) and an adaptation of relief for attribute estimation (ReliefFAttributeEval) evaluation method are used.

@@

However, as in the case of new books only some descriptive data are available %FERGU: data es plural. is->are
(compared to those cases in which historical data on sales of published books 
is available), not all forecasting methods can be used in this specific problem.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
When a new book is launched the publisher faces the problem of
how many books should be printed for delivery to bookstores. Printing too many is the main issue,
since it implies a loss of investment due to inventory excess. In this
paper, we are tackling the problem of predicting total sales in order to 
print the right amount of books, doing so even before the book has
reached the shelves. 
Several years 
% Antonio - Decir cuántos años son, que no me acuerdo.
of data on published books in Spain have been processed by means of data visualisation and other feature selection techniques. The aim is to find out what are the variables that have more impact on sales, and then use machine learning and forecasting methods to predict sales, and, from them, estimate the print-run.
The described methodology improves the forecasting running time and is eventually able to predict sales with remarkable accuracy. Moreover, the proposed method has been validated by the company that provided the data and incorporated in a business intelligence tool for publishers,
since the obtained models provide a reliable guidance on the decision process of
publishing a book, without human intervention 
either for the operation or for interpretation.
% Antonio - esto es cierto??? :D
\end{abstract}

@@

Publishing a book, as releasing any other product, implies several
types of risks and costs due to
the complexity and derived expenses of the production and distribution processes. 
% tienes que enmarcar el problema. Se trata de productos culturales
% con soporte físico y con ventas relativamente pequeñas. Libros,
% discos, no sé si alguna cosa más. - JJ
A newly launched product could be, additionally, completely new to the company (not a new version or edition of a previous product), and sales forecasts can
only be based on the experience of other similar products. 
In this scope, having accurate estimations of future sales of the new
product is extremely important \cite{ChingChin2010}, so that production
runs do not exceed predicted sales. 
Indeed, several studies have demonstrated that improving sales predictions 
(a reduction of forecasting errors) results in an enhancing in the 
%FERGU: an enhancing está bien dicho? Mejor "an enhacement", no?
production process \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.

@@

Book publishers, as well as other content producers, release new {\em
  products} more frequently than other industries, so that they face the
problem of predicting sales quite often. The issue, in this case, is to print an
adequate number of copies but not too many, as the unsold volumes will
lead to losses and sunk inventory cost, 
% Antonio - 'sunk inventory cost' es corecto?
whereas if the number of printed copies was not enough, you can always print more. 
%FERGU: el you ese es muy coloquial, reescribir
% Antonio - Esto habría que matizarlo más, de hecho, decirlo va un poco en contra de nuestro artículo, ya que simplifica el problema. Yo indicaría que errores en predicciones por exceso o por defecto tienen MUCHAS pegas (ambos casos), si bien el exceso es peor, claro, pero decir que lo otro es también muy negativo y por eso hay que ajustar muy bien la predicción. ;)
% Se podría señalar, por ejemplo:
% - repetición de costes de distribución
% - mala impresión al cliente/lector, que pueden repercutir negativamente en las ventas
% - algunas más... :D
In this sense, errors in one or the other direction do not have the same impact, although a temporal scarcity of a book that is selling well is also a problem.
% Antonio - esto habría que rescribirlo de acuerdo a lo anterior que comento. ;)
%FERGU: lo de one or the other direction creo que confunde

Thus, it is extremely important to develop an accurate predictive tool which could accurately forecast the future sales a new book will achieve, in order to optimise production and to improve the publishing company profits or minimise losses \cite{Zhao2001}. This is the main objective of this paper.
%FERGU: entonces el objetivo es desarrollar una herramienta? La metodología? Dejarlo más claro en todos los sitios
An example is the optimisation of sales \cite{Mattila2002} by
improving profit margins by selling the whole print-run. 
% Antonio - podrías extender un poco el ejemplo? Es decir, describir un poco más lo que se hace en ese trabajo. ;)

However, designing such an accurate predictive tool is a difficult task in this scope, as book sales are influenced by several factors that make them fluctuate and, moreover, usually they might be not controllable and even unknown.
%FERGU: "moreover, usually" son dos adverbios juntos y queda un poco raro 
For instance, some are related to decisions on purchases, others with freight 
%FERGU: some factors para dejarlo claro
traffic, or others with the distribution strategy \cite{Little1998}.

Thus, it is very important to know the product and the variables that
might affect the sales, and how an expert manager takes them into account \cite{Armstrong2001,SThomassey2014}. 
                                % ¿Esto también pasa en la industria de la
                                % moda. ¿Qué vamos a usar de esto? - JJ
                                % [Pedro] esto iba referido a la Industria Editorial.
Their impact is difficult to estimate and it is not constant over time, 
hence the difficulty to adequately identify and measure their influence \cite{DeToni2000}.
In addition, some may have correlations between them. 
%FERGU: some ... variables, no?
However, these correlations can be detected using data analysis methods, 
such as Self-Organizing Maps (SOM) \cite{kohonen1998} 
or stepwise regression analysis (SRA) \cite{Chang2009}. % What do they do? What are the results?

In this research, the problem of how many units should be printed 
when a new book is published is faced using data provided by the 
Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}},
a company that provides management systems and services for book shops,
% Antonio - 'libraries' o 'book shops'? Supongo que lo segundo. ;D
publishers and distributors. 
Usually, the company's expert sales managers analysed historical data 
and applied their knowledge using external variables to compute correct estimations (predictions), for instance, she can decide increasing or decreasing the sales prediction based on season or sales period.
                        % varias citas - JJ
                        % [Pedro] lo modifico para comentar quienes nos facilitaron los datos
                        %  y que así era como funcionaban hasta ese momento.
%In any case, in general companies usually use a forecasting model and then, 
%an expert applies his knowledge, as the company might require an 
%interpretable and understandable model. 
However, carrying out the analysis and forecasting process as a human expert,
may lead to a `fuzzy-like' analysis, which may not take all the variables into account. 
%FERGU: fuzzy-like existe? suena raruno :P
In addition, the process might be tedious, especially when the amount
of data is quite large, and even, different experts can reach different
predictions from the same dataset \cite{ChingChin2010,Sanders1994}.

@@

Specifically, Time-Series prediction methods \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990} 
is perhaps the most used technique to tackle the sales forecasting problems. 
The efficiency of these techniques strongly depends on the field of application 
and the correctness of the problem data. However, since they require a large amount of data for predicting sales, these methods are not the most suitable for this task \cite{ChingChin2010}.

@@

For this reason, usually the methods used to predict book sales have been generally based on experts' experience. They analyse data about sales and, taking into account their knowledge in industry, their experience, and their perception about trends, could make decisions on the companies production (how many books should be printed when a new book is published).
%FERGU: quitad los paréntesis :)
This is a complex problem, since the predictions are influenced by external variables that must be taken into account, such as seasonality, promotions or fashions that expert managers might subjectively apply \cite{Lapide1999,ChingChin2010,ChernWSF15}.

  %[pedro] sobre la industria editorial no hay trabajos sobre predicción de ventas.
  % Lo habitual ha sido usar el conocimiento de expertos para realizar predicciones 
  %  o aconsejar acerca de la cantidad de libros a imprimir.
  % Lo más parecido que he encontrado son dos trabajos (uno en realidad) de Moon et al. 
  %  sobre "Use Blog Information As Book Sales Prediction":
  %     Moon2010ICSSSM
  %     Moon2010ICEC
Recently, some works have proposed analyzing relationships between on-line information 
and book sales \cite{Moon2010ICSSSM,Moon2010ICEC}. Specifically, Moon et al. propose using the number of blog references as an indicator of the success of a book, and thus, its sales. Different sales patterns are observed by analysing data obtained.
% Antonio - describir esos 'sales patterns'. ;)
% FERGU: y también cuales son esos 'data obtained'
However, the authors used in these papers historical data from published books, 
so their proposed methodology can not be applied to the problem of unpublished-books sales prediction.
%FERGU: pero nosotros también usamos historical data, no? qué diferencia hay con lo nuestro? por qué lo nuestro es lo mejor?

@@

In order to deal with this issue, i.e. forecasting sales of new products, some authors have used different data mining methods \cite{Hammond1990,Chang2009,ChingChin2010,Thomassey2012,Xia2012}. 
% Antonio - quizá habría que comentar alguno o todos bervemente...
%
In the same line, Thomassey et al. \cite{SThomassey2014} propose using a clustering method together with decision trees for sales forecasting in textile-apparel fashion industry, 
a very similar issue to the new book publishing one.
The same problem was previously faced by Xia et al. \cite{Xia2012} using a 
forecasting method based on extreme machine learning with adaptive metrics of inputs.
% Antonio - of -> as???
The complexity of this problem relies on the lack of historical data, on the short lifetime of the majority of items, 
% Antonio - ver si está bien el cambio 'large number' -> 'majority'
and on the influence of variables such as promotions, fashions, or economic environment \cite{Thomassey2012,Xia2012,SThomassey2014}, as mentioned above.
%FERGU: completar con: "In our case, these ideas ..."

  %[Pedro] otro caso muy similar es el paper de ChingChin2010 sobre:
  % New tea product
  % New cosmetic product
  % New soft drink product
In \cite{ChingChin2010}, a decision-support system for new product sales %FERGU: The work of Chinchin et al.?
forecasting is proposed to solve three real-world sales forecasting problems, namely: new tea, cosmetics, and soft drink products. This is addressed taking into account quantitative variables.
% Antonio - qué significa eso?
In that study, products are classified based on their sales patterns, so it is assumed that products in the same class would follow a similar sales pattern. 
However, as the authors state, the proposed system can not deal with qualitative 
data related to the products. Moreover, real-world cases, such as consumer 
electronics and fashion products, should be deeply analyzed, as these industries 
present/launch new products every season.

@@

The main objective of this paper is to forecast sales for 
%FERGU: el objetivo es la herramienta o la predicción?
unpublished books for which no historical data are available. Instead, just some
%FERGU: pero usamos datos históricos de otros para la predicción, no? Como otros papers...
descriptive and variables known in advance related to the new book. In order to do that, we have used a training dataset which includes historical sales data for a big amount of books published in Spain for several years, with a set of 50 features or variables per pattern.

@@

In this prediction problem there are other external variables that also affect 
the sales of a new book, such as those related to seasonality, trends or 
promotions, that classical prediction methods can not deal with. %FERGU: por qué?
However, an expert can consider them to modify the forecast obtained by 
the automatic method. Even publishing companies tend to define rules or 
indexes to subjectively adjust the results of prediction based on
external data. 
Thus, the proposed method, will analyse the provided data and variables and will yield a forecast of sales according to them. This result could be used as a reference for a human expert, who would consider it in his/her own prediction process.

@@

There is no a standard methodology to solve the general problem of sales forecasting. %FERGU: hacer más hincapié de esto en la intro entonces
In this work we have followed these steps: %FERGU: por qué estos steps y no otros? Ponerlo aquí. Esta metodología es general o solo para este paper?
%\hspace{2cm}
\begin{verbatim}
  Step 1: Collect and analyse data
       - Data preprocessing
       - Feature selection
  Step 2: Select the best forecasting method
       - Evaluate forecasting models
       - Perform forecast
  Step 3: Subjectively adjust obtained results
      - Apply additional expert knowledge, such as information 
        about seasonality or trends.
\end{verbatim}

@@

Then, a Feature Selection process \cite{kittler1986feature} is carried out, as it is an effective dimensionality reduction technique and an essential preprocessing method to remove `noisy' (non-useful) features \cite{Krishnapuram2004}. The aim of these algorithms is exploring the space of attributes to find out which subset of them yield the best results in a classification or prediction problem.
  In this stage, both, numerical and visualisation-based approaches have been applied, in order to select the best variables for the forecasting methods.
  This task may also help to identify leading indicators to be considered by a human expert to make predictions.

After this process, several forecasting methods have been tested, considering different approaches, such as rule- or tree-based, together with numerical methods. 
% Antonio - is 'numerical' the best term for these kind of methods?
%FERGU: OJO que en esta sección a veces usáis el presente perfecto (have been) y otras el presente (is performed)
The obtained results are then compared.

@@

In the literature different error measures can be found to evaluate the results obtained using the prediction methods \cite{ChingChin2010,Madsen2008}. 
Those error measurements are also called error functions or cost functions. 
%One of the most commonly used is the mean absolute error (see equation \ref{eq:MAE}).
We have used the widely accepted standard equations \cite{gepsoft} in order to compare the obtained results with those presented in other research papers using other methods.
That is why different standard error measurements (Equations \ref{eq:MAE} to \ref{eq:RRSE}), implemented in tools like Weka \cite{pentaho,Witten2011} 
or R \cite{otexts,Hyndman2013}, are considered.
Specifically, in order to compute the forecasting errors of the different methods, Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute error (RAE) and Root relative squared error (RRSE) have been selected:
%FERGU: have been selected for this methodology, for this work... algo así

@@

%FERGU: poner aquí algo de un párrafo que explique como se valida la metodología

%-------------------------------------------------
\subsection{Data collection and analysis}
%FERGU: The first step in our methodology is...

@@

Feature extraction is a ``transformation-based approach'', therefore it transforms the original meaning of the features. This approach involves creating a subset of new features by combinations of the existing features, thus it is employed when the semantics of the original dataset will not be needed by any future process. On the contrary, feature selection attempts to retain the meaning of the original feature set. It is part of what is called semantic-preserving techniques, known as ``selection-based approaches". By searching through all possible combinations of features, the aim of these techniques is to determine a minimal feature subset to reduce processing time, while obtaining the same or higher accuracy as the initial feature set \cite{liu1998feature}. In the problem this work assesses, it is very important to maintain the semantics of the set of initial variables, and therefore several feature selection methods have been applied.

@@

SOMs (and U-Matrix) are usually applied to visualise natural structures in the data and their relations, as well as the natural groupings that could be among them. In addition, SOM makes easy the estimation of the variables that have more influence on these groupings. Other statistical and soft computing tools can also be used for this purpose, but since Kohonen's SOMs offers a visual way of doing it, it is much more intuitive, and takes advantage of the capabilities of the human brain as a pattern recogniser.
%FERGUSON: por qué se menciona aquí la palabra "Kohonen" y no antes?

@@

As far as the feature selection methods are concerned, Weka separates the process into two parts:
%FERGU: por qué mencionamos a Weka aquí y no antes?
\begin{itemize}
  \item Attribute evaluator: This is the method by which the feature subsets are assessed. In this work, both a correlation-based feature subset evaluation method (CfsSubsetEval) and an adaptation of relief for attribute estimation (ReliefFAttributeEval) evaluation method are used.

@@

However, as in the case of new books only some descriptive data are available 
(compared to those cases in which historical data on sales of published books 
is available), not all forecasting methods can be used in this specific problem.
